### 2019-11-29 thesis/txt/2-models.tex
updated model graphics and dev mail screenshot

\begin{table}[htbp]
\centering
\caption{Chunk Retrieval Techniques}
\begin{tabularx}{\textwidth}{@{}XlXlX@{}} 
\toprule
Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
\midrule
Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / Output Examples      \\
Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output Examples           \\
Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, Context Length  \\
Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
Diff Approach                &         & Line not present in successful log, informatino retrieval  & Line        & Successful Log File       \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table}

>>>>

\begin{table}[htbp]
\centering
\caption{Chunk Retrieval Techniques}
\begin{tabularx}{\textwidth}{@{}XlXlX@{}} 
\toprule
Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
\midrule
Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In / Output Examples      \\
Common Text Similarity       & CTS     & Tf-idf \& cosine similarity, mean number of lines expected & Line        & Output Examples           \\
Keyword Search               & KWS     & Keywords, mean number of lines expected                    & Line        & Keywords, Context Length  \\
Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval Length          \\
Diff Approach                &         & Line not present in successful log, information retrieval  & Line        & Successful Log File       \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table}

### 2019-11-29 thesis/txt/6-discussion.tex
updated model graphics and dev mail screenshot

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
		\label{fig:crt-recommendation}
\end{figure}

@@

\paragraph{Implementation}
Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
Our implementation of PBE is mainly based on the program synthesis provided by PROSE\@.
Its limitations are therefore also mainly influenced by this library.
For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with (too many?) top level OR operators. \mention{CITATION NEEDED}
This limitation was necessary to keep the synthesis performance reasonable.

@@

\paragraph{Training Set Size}
Especially the results for CTS are influenced by the fact that we only trained on one to five examples.
Information retrieval techniques commonly learn on larger data sets. \mention{CITATION NEEDED}
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.

>>>>

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/crt-recommendation.pdf}
		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
		\label{fig:crt-recommendation}
\end{figure}

@@

\paragraph{Implementation}
Our results are highly dependent on our implementation of the investigated chunk retrieval techniques and the libraries we used.
Our implementation of PBE is mainly based on the program synthesis provided by PROSE\@.
Its limitations are therefore also mainly influenced by this library.
For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with arbitrary boolean conjunctions and disjunctions~\cite{mayer2015user}.
This limitation was necessary to keep the synthesis performance reasonable.

@@

\paragraph{Training Set Size}
Especially the results for CTS might influenced by the fact that we only trained on one to five examples.
We chose this small training set size as the training examples have to be provided per repository and we expect a developer to not want to provide more examples than the small numbers we evaluated on.
